### 2019-04-02 Thesis/games.tex
Did another big fuck-off diagram.

Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
\[
  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
  \]
Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
\[
  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
  \]
We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
\[
  \begin{tikzcd}
    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
      & \Varr \sequoid \oc\Varr
  \end{tikzcd}
  \]
Concretely, the strategy $\cell$ behaves as follows.  
When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.

@@

      Now we have a commutative diagram
      \begin{figure}[htbp]
        \[
          \begin{tikzcd}[column sep=41pt, row sep=30pt]
            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc n" description] \arrow[dr, Rightarrow, no head]
              & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" description]  \\
            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
              & I \arrow[l, "\oc n" description]
                & \Varr \sequoid \oc\bN \arrow[d, "\Varr\sequoid\cell" description] \arrow[dd, "\pr_n\sequoid\oc\bN" {description, pos=0.44}, controls={+(-2.5,-0.2) and (-0.5,0.5)}]
                  & \Varr \tensor \oc\Varr \arrow[dl, "{\wk_{\Varr,\oc\Varr}}" description] \arrow[dd, "\pr_n\tensor\oc\Varr" description] \\
            %
              & \bC \tensor \oc\bN \arrow[dr, "{\wk_{\bC,\oc\bN}}" description] \arrow[ddr, "\bC \tensor \cell" description]
                & \Varr \sequoid\oc\Varr \arrow[ddr, "\pr_n\sequoid\oc\Varr" description]
                  & \\
            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\oc\Varr}" description]
              & I \tensor \oc\bN \arrow[u, "\skipp\tensor\oc\bN" {description, pos=0.44}] \arrow[d, "I\tensor \cell" description]
                & \bC \sequoid \oc\bN \arrow[dr, "\bC \sequoid \cell" description]
                  & \bC \tensor \oc\Varr \arrow[d, "{\wk_{\bC,\oc\Varr}}" {description, pos=0.44}] \\
            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
              & I \tensor \oc\Varr \arrow[r, "\skipp \tensor \oc\Varr"']
                & \oc\bC \tensor \oc\Varr \arrow[r, "{\wk_{\bC,\oc\Varr}}"']
                  & \bC \sequoid \oc\Varr
          \end{tikzcd}
          \]
      \end{figure}
  \end{itemize}
\end{proof}

>>>>

Given $n\in\bN$, we define a strategy $\wwrite_n\from \oc\bN \implies \bC \sequoid\oc\bN$ by
\[
  \wwrite_n = \oc\bN \xrightarrow{()} I \xrightarrow{\skipp\tensor \oc n} \bC \tensor \oc\bN \xrightarrow{\wk} \bC \sequoid\oc\bN\,.
  \]
Let $\rread \from \oc\bN \implies \bN \sequoid \oc\bN$ be the morphism part $\alpha$ of the limiting coalgebra.  
In other words, by Proposition \ref{PropFormulaForAlpha}, $\rread$ is the composite
\[
  \rread = \oc\bN \xrightarrow{\mu_\bN} \oc\bN \tensor \oc\bN \xrightarrow{\der_\bN\tensor\oc\bN} \bN \tensor \oc\bN \xrightarrow{\wk_{\bN,\oc\bN}} \bN \sequoid\oc\bN\,.
  \]
Then we get a coalgebra $\cell_0\from \oc \bN \implies \Varr \sequoid \oc \bN$ given by
\[
  \oc\bN \xrightarrow{\langle (\wwrite_n)_{n\in\bN}, \rread\rangle}
  (\bC \sequoid \oc\bN)^{\bN} \times (\bN \sequoid \oc\bN) \xrightarrow{\dist_{(\bC)_{\bN},\bN,\oc\bN}\inv}
  (\bC^\bN \times \bN) \sequoid \oc\bN = \Varr \sequoid \oc \bN\,.
  \]
We then take the anamorphism $\cell=\fcoal{\cell_0}\from \oc\bN \implies \oc\Varr$; i.e., $\cell$ is the unique morphism making the following diagram commute.
\[
  \begin{tikzcd}
    \oc\bN \arrow[r, "\cell_0"] \arrow[d, "\cell"']
      & \Varr \sequoid \oc\bN \arrow[d, "\Varr \sequoid \cell"] \\
    \oc\Varr \arrow[r, "\alpha_{\Varr}"]
      & \Varr \sequoid \oc\Varr
  \end{tikzcd}
  \]
Concretely, the strategy $\cell$ behaves as follows.  
When player $O$ plays in $\oc\Var$, he chooses to play either in one of the copies of $\bC$ or in $\bN$.  
If he plays the initial move $q_n$ in the $n$-th copy of $\bC$, player $P$ updates the value she has stored in her head to $n$.  
If he plays the initial move $q$ in $\bN$, then player $P$ replies with this stored value.  
Lastly, if he plays this initial move $q$ without having played in any of the copies of $\bC$, then player $P$ interrogates the argument in order to find out which value to play.

@@

      Now we have a commutative diagram
      \begin{figure}[htbp]
          \begin{tikzcd}[column sep=41pt, row sep=30pt]
            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc n" description] \arrow[dr, Rightarrow, no head]
              & \oc \bN \arrow[r, "\cell"] \arrow[d, "()" description] \arrow[dr, "\cell_0" description]
                & \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[dd, "\alpha_{\Varr}" description, controls={+(1,-0.25) and +(0.8,0.75)}, start anchor={[yshift=-1pt]}, end anchor = {[xshift=25pt]}]
                  & \oc \Varr \tensor \oc \Varr \arrow[d, "\der_{\Varr} \tensor \oc\Varr" description]  \\
            \oc\bN \arrow[dd, "\cell" description] \arrow[ddr, "\lunit_{\oc\bN}" description, end anchor={[xshift=-3pt, yshift=-2pt]}]
              & I \arrow[l, "\oc n" description]
                & \Varr \sequoid \oc\bN \arrow[d, "\Varr\sequoid\cell" description] \arrow[dd, "\pr_n\sequoid\oc\bN" {description, pos=0.44}, controls={+(-2.5,-0.2) and (-0.5,0.5)}]
                  & \Varr \tensor \oc\Varr \arrow[dl, "{\wk_{\Varr,\oc\Varr}}" description] \arrow[dd, "\pr_n\tensor\oc\Varr" description] \\
              & \bC \tensor \oc\bN \arrow[dr, "{\wk_{\bC,\oc\bN}}" description] \arrow[ddr, "\bC \tensor \cell" description]
                & \Varr \sequoid\oc\Varr \arrow[ddr, "\pr_n\sequoid\oc\Varr" description]
                  & \\
            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\oc\Varr}" description]
              & I \tensor \oc\bN \arrow[u, "\skipp\tensor\oc\bN" {description, pos=0.44}] \arrow[d, "I\tensor \cell" description]
                & \bC \sequoid \oc\bN \arrow[dr, "\bC \sequoid \cell" description]
                  & \bC \tensor \oc\Varr \arrow[d, "{\wk_{\bC,\oc\Varr}}" {description, pos=0.44}] \\
            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
              & I \tensor \oc\Varr \arrow[r, "\skipp \tensor \oc\Varr"']
                & \oc\bC \tensor \oc\Varr \arrow[r, "{\wk_{\bC,\oc\Varr}}"']
                  & \bC \sequoid \oc\Varr
          \begin{tikzcd}[row sep=30pt]
            I \arrow[r, "\oc s(x)"] \arrow[d, "\oc s(x)" description] \arrow[dr]
              &[-31pt] \oc\bN \arrow[r, "\cell"] \arrow[dr, "\mu_\bN" description] \arrow[ddr, "\cell_0" {description, near end}, bend left=50]
                &[-100pt] \oc\Varr \arrow[r, "\mu_{\Varr}"] \arrow[ddd, "\alpha_{\Varr}" description]
                  &[-21pt] \oc\Varr \tensor \oc\Varr \arrow[d, "\der_{\Varr}\tensor\oc\Varr" description] \\
            |[alias=Z]| \oc\bN \arrow[d, "\lunit_{\oc\bN}" description] \arrow[dd, "\cell" description]
              & |[left=40pt of Z.east]| I \tensor I \arrow[dl, "I \tensor \oc s(x)" description] \arrow[r, "\oc s(x) \tensor \oc s(x)"] \arrow[d, "s(x)\tensor \oc s(x)" description]
                & |[left=50pt of Z.west]| \oc \bN \tensor \oc\bN \arrow[dl, "\der_\bN \tensor \oc\bN" description]
                  & \Varr \tensor \oc\Varr \arrow[ddl, "{\wk_{\Varr,\oc\Varr}}" {description, pos=0.65}] \arrow[dd, "\pr_{\bN}\tensor\oc\Varr" description] \\
            |[right=of Z.west]| I \tensor \oc\bN \arrow[r, "s(x)\tensor\oc\bN"'] \arrow[ddr, "I \tensor \cell" description]
              & \bN \tensor \oc\bN \arrow[d, "{\wk_{\bN,\oc\bN}}" description] \arrow[ddr, "\bN \tensor\cell" {description, pos=0.4, xshift=-5pt}, bend right=30]
                & |[left=of Z]| \Varr \sequoid \oc\bN \arrow[dl, "\pr_\bN \sequoid \oc\bN" {description, pos=0.65}, bend left=30] \arrow[d, "\Varr\sequoid\cell" {description, xshift=-5pt}, bend left=30]
                  & \\
            \oc\Varr \arrow[d, "\mu_{\Varr}" description] \arrow[dr, "\lunit_{\Varr}" description]
              & |[right=of Z]| \bN \sequoid \oc\bN \arrow[drr, "\bN \sequoid \cell" {description, pos=0.4}, controls={+(0.2,-1.2) and +(-0.3,0.2)}, to=Y.north west, end anchor={[yshift=-2pt]}]
                & \Varr \sequoid\oc\Varr \arrow[dr, "\pr_\bN \sequoid \oc\Varr" {description, pos=0.35}]
                  & \bN \tensor \oc\Varr \arrow[d, "{\wk_{\bN},\oc\Varr}" description] \\
            \oc\Varr \tensor \oc\Varr \arrow[r, "()\tensor\oc\Varr"']
              & I \tensor \oc\Varr \arrow[r, "s(x)\tensor\oc\Varr"']
                & \bN \tensor \oc\Varr \arrow[r, "{\wk_{\bN,\oc\Varr}}"']
                  & |[alias=Y]| \bN \sequoid \oc\Varr
